### 2010-06-30 paper/IIWAS2010/content/system_arch.tex
Joir-dan updated the system_arch section

This section presents ontology and copora, query processing, ranking queries, and query executing.

@@

Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies. This approch is motivated by YAGO \cite{Suchanek2009phd}. First a realm is mapped to a DBpedia category \cite{Bizer2009}. 
Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}. From here, the system recursively includes all categories up to the root.

@@

@@

The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser
used to track the search pathways to an answer for a \textit{path-finders} query. It
also helps guide to identify categories (optional) for the query terms. 
Morpheus has two types of categories: \emph{input categories} and \emph{output categories}.
Input categories annotates the query terms into a class or category, which are 
useful in finding similar queries. On the other hand, output categories give hints
to the expected answer of a user query. Morpheus captures all
this query information in the representation of an SSQ. For example, suppose, a guide 
tries to answer the query ``A 1997 Toyota Camry V6 needs what size tires?'', using
Morpheus. With the help of the QRR, guide may choose relevant query terms and assign
\emph{input categories} to them: Toyota : manufacturer, Camry V6 : 
model, tire : automotive parts, and size as the \emph{output category}. 
In addition, guide can log the search pathways to an answer (e.g. P215/60R16)
to this query and select the query \emph{realm} as automotive.

The \emph{Query Resolution Method} (QRM) is a data structure that models the
question answering process. A QRM is usually constructed by a \emph{guide} with
the help of the QRR. Each QRM contains an \emph{ontological realm}, an SSQ, and
information to support the query answering process. QRMs are associated with an
ontology that has a particular realm i.e. an ontological realm. In addition, 
the QRM contains information required to visit each page needed to 
answer the query as well as the order of visitation. For each
dyanamic page, it stores the list of inputs to the URL such as form inputs and
the possible referrence outputs (highlighted portions of the web page).

% NLP arch. 
% Joir-dan

Rather than working blindly, forming all possible n-grams from the query 
and running probabilities, it seemed to be a better approach to identify 
important noun phrases within the query, and work with those. Using our 
query parser, we proceed to tokenize, parse, and chunk our candidate query, 
extracting verb groups, answer classes, and descriptive info from each query. 
In the example query "What is the tire size of a 1997 Toyota Camry?," 
the verb group is the verb "is," the answer class is "tire size," and descriptive 
info is "of a 1997 Toyota Camry." The next step is to create n-grams from these chunks. 
Using these n-grams, we will query our database for frequencies associated with 
each n-gram: overall frequency and categorical frequency, alongside category 
term count and overall term count, to calculate categorical probabilities 
and establish a realm for the candidate query, choosing realm with highest probability.

@@

We consider the category match as a type match and we use 
\emph{category divergence} to calculate the relevance between 
the candiate SSQ and a qualified SSQ. Each qualified SSQ will 
have input terms, output terms, and associated classes, and one realm (from QRM). 
For the candidate SSQ, the relevant categories for terms 
are determined from the NLP engine and corpora. The calculation of a realm 
for a candidate query is done using the n-grams found within said query 
and the probabilities (if any) found using frequencies within the database.
We match QRMs that belong to the same \emph{realm} of the candidate SSQ. 
The relevance of a qualified SSQ to the candidate SSQ is 
determined by aggregating the divergence measure of input-term-categories 
associated with them. In addition, we order QRMs in the data store 
by descreasing relevance. The order provides a ranking for the results 
to the user. The following subsection describes \emph{category divergence} 
in detail.

>>>>

% This was corrected in my version... (Joir-dan performing diff 2010-06-30)
This section presents ontology and corpora, query processing, ranking queries, and query executing.

@@

%% Comment made by Joir-dan (2010-06-29)
 %%Need to remove any references to Markov Blanket... since we abandoned that ship a while ago...

Morpheus uses the DBpedia categories, Wikipedia pages and the WordNet synset heterarchy to construct ontologies. This approach is motivated by YAGO \cite{Suchanek2009phd}. First a realm is mapped to a DBpedia category \cite{Bizer2009}. 
Then a \emph{Markov Blanket} \cite{PRIS} is created covering all neighboring categories and using the DBpedia ontology properties \emph{broader} and \emph{narrower}. From here, the system recursively includes all categories up to the root.

%% ^^^ Needs to remove references to blanket

@@

%% Comment by Joir-dan 2010-06-30: Term should prolly be replaced by n-gram

@@

%% Was edited and shortened by Joir-dan and Wilson (2010-06-29)
The \emph{Query Resolution Recorder} (QRR) is an instrumented web browser that records the interactions of a path-finder answering a question. The path-finder also uses the tool to identify ontological categories associated with search terms. Morpheus stores the query together with its terms and categories as an SSQ (Figure \ref{fig:ssq_example}). Using the QRR, the path-finder is also able to identify where answers can be found within traversed pages.

%% Was added by Joir-dan and Wilson (2010-06-29)... but may need to be better formatted
\begin{figure}[t]
\label{fig:ssq_example}
("An  1997 Toyota Camry V6 has what size tires", 
     (1997: Date, Toyota: Manufacturer, Camry: Model, V6: Engine ),
     (tire: Part, size: Measurement))

%% Comment made by Joir-dan Gumbs (2010-06-29) 
%%Need to talk a bit about this SSQ Structure: Does anyone see anything wrong with this representation?
\caption{An example SSQ for the question: A 1997 Toyota Camry V6 has what size tires?}
\end{figure}

%% Edited by Joir-dan and Wilson (2010-06-29)
The \emph{Query Resolution Method} (QRM) is a data structure that models the
question answering process. A QRM represents a generalized executable realization of the search process that the path-finder followed. The QRM is able to reconstruct the page search path followed by the path-finder. Each QRM contains an \emph{ontological realm}, an SSQ, and information to support the query answering process. For each dynamic page, it stores the list of inputs to the URL such as form inputs and the possible reference outputs (highlighted portions of the web page).

% NLP arch. 
% This may need to be moved somewhere... but not sure where.... Joir-dan Gumbs (2010-06-29)

Queries inserted by path-followers take a different approach. The Morpheus search system parses, tags, and processes the queries in order to pull important n-grams. The system then assigns the most probable realm to the query using \textit{realm}|\textit{n-gram} priors calculated from realm-specific corpora. Once the realm is assigned, an ontology search is performed to assign classes to the n-grams. An SSQ is constructed and the system attempts to match this SSQ to a query path created by a path-finding user. Rather than matching n-grams, the goal is to match input and output classes, since the paths can potentially answer similar queries.

@@

We consider the category match as a type match and we use 
\emph{category divergence} to calculate the relevance between 
the candidate SSQ and a qualified SSQ. Each qualified SSQ will 
have input terms, output terms, and associated classes, and one realm (from QRM). 
For the candidate SSQ, the relevant categories for terms 
are determined from the NLP engine and corpora. The calculation of a realm 
for a candidate query is done using the n-grams found within said query 
and the probabilities (if any) found using frequencies within the database.
We match QRMs that belong to the same \emph{realm} of the candidate SSQ. 
The relevance of a qualified SSQ to the candidate SSQ is 
determined by aggregating the divergence measure of input-term-categories 
associated with them. In addition, we order QRMs in the data store 
by decreasing relevance. The order provides a ranking for the results 
to the user. The following subsection describes \emph{category divergence} 
in detail.
